Current and future constraints on primordial magnetic fields

### 2015-11-05 pmf.tex
TEST
Added the details of code and parameters

>>>>

The PMF power spectra are computed by a modified code CMBACT\footnote{\url{http://www.sfu.ca/~levon/cmbact.html}} with parameters $B_{\rm{1Mpc}}$=2.5 \rm{nG}, $n_s$=-2.9 and $a_{\nu}/a_{\rm{PMF}}$=$10^9$. They are used as a template of PMF power spectrum calculation, i.e., the new PMF power spectra with different amplitudes $B_{\rm{1Mpc}}$ are derived from a simply scaling law.
